Variable Selection

### 2015-06-28 var_select.rmd
added client.age variable

Try running a cforest over night with full dataset - don't include 
```

@@

@@

>>>>

@@

# New Variable - client age

```{r, echo=FALSE}
#read csv file with all the client details - want to merge this with client df
details<- read.csv('17marchclients.csv',
                   na.strings = c("", " ", "NA"))
head(details)
#delete client.contact, client.count, and contact.count columns
details<- details[,c(1,5:9)]
#rename columns
names(details)[2]<- 'Business'
names(details)[4]<- 'Biz.size'
names(details)[5]<- 'Biz.type'
names(details)[6]<- 'Biz.age'

#delete rows with 4 NA values
details<-details[rowSums(is.na(details))!=5,]
details<-details[rowSums(is.na(details))!=4,]

#add row for client code
code.client<- read.csv('code_client2.csv')[,-1]
details<- merge(details, code.client, by.x ='client', by.y ='client2', all.x=TRUE, all.y=FALSE)
details<- transform(details, client.age = 2014- Biz.age)

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)

@@

Use cforest to test remaining variables (with significant NA components)

These include:

* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Primary
* Job.Detail.Secondary
* Job.Type.Primary
* Job.Type.Secondary
* Type
* Project.Value
* no.employees
* client age????
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age

First eliminate some of the job.detail.secondary - that kind of thing
Then see if any have matching NA rows
Then run cforest on each variable individually
